---
title: "Unsolved Homicide Report"
output: pdf_document
---
  
  *All data sourced from the Murder Accountability Project - http://www.murderdata.org/
  
```{r global.options, include=FALSE}

knitr::opts_chunk$set(echo=FALSE,
                      warning=FALSE)
```

```{r Loading-Library, include=FALSE}

#Packages
library(dplyr)
library(tidyverse)
library(tinytex)
library(ggplot2)
library(gridExtra)
library(float)
library(ggplot2)
library(knitr)

```

```{r General-Homicide-Tables,include=FALSE}

#this is the general homicide overview

total_homi <- supp_homi_fips %>%
  filter(State==i)%>%
  mutate(min_year = input$years[1])%>% #Taking max and min year from selected input
  mutate(max_year = input$years[2]) %>%
  #mutate(min_year=2010)%>% #For Testing
  #mutate(max_year=2019)%>% #For Testing
  filter(Year >= min_year & Year <= max_year)%>%
  mutate(unsolved_homi=sum(Solved=='No'))%>% #sum of unsolved
  mutate(solved_homi=sum(Solved=='Yes'))%>% #sum of solved
  mutate(count=1)%>% #case count
  mutate(homicide_total=sum(count))

#organized for graphing
solve_graph <- select(total_homi, Unsolved=unsolved_homi, Solved=solved_homi)%>%
  gather(Unsolved, Solved, key='Case Outcome', value='Total')%>%
  unique()%>%
  mutate(x='Homicide Cases')

#subsetting homicount and clear rate
homi_count <- sum(total_homi$solved_homi[[1]], total_homi$unsolved_homi[[1]])

clear_rate <- round((total_homi$solved_homi[[1]]/homi_count)*100,2)

#this is the sex section
vic_sex <- select(supp_homi_fips,Year,State,VicSex)%>%
  filter(State==i)%>%
  mutate(min_year = input$years[1])%>% #Taking max and min year from selected input
  mutate(max_year = input$years[2]) %>%
  #mutate(min_year=2010)%>% #For Testing
  #mutate(max_year=2019)%>% #For Testing
  filter(Year >= min_year & Year <= max_year)%>%
  mutate(Male_Vic = sum(VicSex=='Male'))%>%
  mutate(Female_Vic = sum(VicSex=='Female'))%>%
  mutate(Unknown_Vic = sum(VicSex=='Unknown'))%>%
  unique()

#organized for victim sex graph
sex_graph <- select(vic_sex, Male=Male_Vic,Female=Female_Vic, Unknown=Unknown_Vic)%>%
  gather(Male,Female,Unknown, key='Victim Sex', value='Total')%>%
  unique()

#offender sex
off_sex <- select(supp_homi_fips,State,OffSex, Year) %>%
  filter(State==i)%>%
  mutate(min_year = input$years[1])%>% #Taking max and min year from selected input
  mutate(max_year = input$years[2]) %>%
  #mutate(min_year=2010)%>% #For Testing
  #mutate(max_year=2019)%>% #For Testing
  filter(Year >= min_year & Year <= max_year)%>%
  mutate(`Male Offender`=sum(OffSex=='Male'))%>%
  mutate(`Female Offender`=sum(OffSex=='Female'))%>%
  mutate(`Offender Sex Unknown`=sum(OffSex=='Unknown'))

#subsetting offender sex values
male_off <- off_sex$`Male Offender`[[1]]
female_off <- off_sex$`Female Offender`[[1]]
unknown_off <- off_sex$`Offender Sex Unknown`[[1]]

#offender sex graph
off_sex_graph <- select(off_sex, Male=`Male Offender`, Female=`Female Offender`, `Sex Unknown`=`Offender Sex Unknown`)%>%
  gather(`Male`,`Female`,`Sex Unknown`, key='Offender Sex', value='Offender Total')%>%
  unique()

#putting min/max years into values
min_year <- input$years[1]
max_year <- input$years[2]

#min_year <- 2010
#max_year <- 2019

```

# State of `r i` `r min_year` to `r max_year`

## Homicide Statistics from `r total_homi$min_year[[1]]` to `r total_homi$max_year[[1]]`

There have been `r homi_count` homicides since `r total_homi$min_year[[1]]`. A total of `r total_homi$unsolved_homi[[1]]` remain unsolved. The homicide clearance rate is `r clear_rate`%. Figure 1 below shows the total cases broken down by solved and unsolved. This does not represent the number of victims. Homicide cases may include more than one victim or offender.


```{r Clearance-graph-all, fig.width=6, fig.height=4}

ggplot(data=solve_graph, aes(x=x, y=Total, fill=forcats::fct_rev(`Case Outcome`))) + geom_histogram(stat='identity') + theme_classic() + xlab('') +
  geom_text(aes(x=x,y=Total,label=Total), position=position_stack(vjust=.5)) + ggtitle(paste('Figure 1. Homicide Case Clearance', total_homi$min_year[[1]], 'to', total_homi$max_year[[1]])) + labs(fill='Case Outcome') + ylab('Total Homicide Cases') + theme(plot.title=element_text(size=10))

```

\newpage

## Unsolved by Race and Sex - `r total_homi$min_year[[1]]` to `r total_homi$max_year[[1]]`

```{r Unsolved-Tables, include=FALSE}

#A table with the sum of the victims and murder weaposn in unsolved homicide cases

unsolved_homis <- supp_homi_fips %>%
  filter(State==i)%>%
  mutate(min_year = input$years[1])%>% #Taking max and min year from selected input
  mutate(max_year = input$years[2]) %>%
  #mutate(min_year=2010)%>% #For Testing
  #mutate(max_year=2019)%>% #For Testing
  filter(Year >= min_year & Year <= max_year)%>%
  filter(Solved=='No')%>% #keeping only unsolved homicides
  mutate(Female=sum(VicSex=='Female'))%>%
  mutate(Male=sum(VicSex=='Male'))%>%
  mutate(Unknown=sum(VicRace=='Unknown'))%>%
  mutate(White=sum(VicRace=='White'))%>%
  mutate(`American Indian or Alaskan Native`=sum(VicRace=='American Indian or Alaskan Native'))%>%
  mutate(Black=sum(VicRace=='Black'))%>%
  mutate(Asian=sum(VicRace=='Asian'))%>%
  mutate(`Unknown Race`=sum(VicRace=='Unknown'))%>%
  mutate(`Native Hawaiian or Pacific Islander`=sum(VicRace=='Native Hawaiian or Pacific Islander'))%>%
  #White victims
  mutate(`Female White`=sum(VicSex=='Female'&VicRace=='White'))%>%
  mutate(`Male White`=sum(VicSex=='Male'&VicRace=='White'))%>%
  mutate(`Unknown White`=sum(VicSex=='Unknown'&VicRace=='White'))%>%
  #American Indian/Native Alaskan Victims
  mutate(`Female A.I./A.N.`=sum(VicSex=='Female'&VicRace=='American Indian or Alaskan Native'))%>%
  mutate(`Male A.I./A.N.`=sum(VicSex=='Male' & VicRace=='American Indian or Alaskan Native'))%>%
  mutate(`Unknown A.I./A.N.`=sum(VicSex=='Unknown' & VicRace=='American Indian or Alaskan Native'))%>%
  #Black Victims
  mutate(`Female Black`=sum(VicSex=='Female'&VicRace=='Black'))%>%
  mutate(`Male Black`=sum(VicSex=='Male' & VicRace=='Black'))%>%
  mutate(`Unknown Black`=sum(VicSex=='Unknown'&VicRace=='Black'))%>%
  #Asian Victims
  mutate(`Female Asian`=sum(VicSex=='Female'&VicRace=='Asian'))%>%
  mutate(`Male Asian`=sum(VicSex=='Male' & VicRace=='Asian'))%>%
  mutate(`Unknown Asian`=sum(VicSex=='Unknown' & VicRace=='Asian'))%>%
  #Unknown Victims
  mutate(`Female Unknown Race`=sum(VicSex=='Female'& VicRace=='Unknown'))%>%
  mutate(`Male Unknown Race`=sum(VicSex=='Male'& VicRace=='Unknown'))%>%
  mutate(`Unknown Unknown Race`=sum(VicSex=='Unknown' &VicRace=='Unknown'))%>%
  #Native Hawaiian/Pacific Islander
  mutate(`Female N.H./P.I.`=sum(VicSex=='Female'&VicRace=='Native Hawaiian or Pacific Islander'))%>%
  mutate(`Male N.H./P.I.`=sum(VicSex=='Male' & VicRace=='Native Hawaiian or Pacific Islander'))%>%
  mutate(`Unknown N.H./P.I.`=sum(VicSex=='Unknown' & VicRace=='Native Hawaiian or Pacific Islander'))%>%
  #Weapon sums
  mutate(Handgun=sum(Weapon=='Handgun - pistol, revolver, etc'))%>%
  mutate(`Knife or Cutting Instrument`=sum(Weapon=='Knife or cutting instrument'))%>%
  mutate(`Other`=sum(Weapon=='Other or type unknown'))%>%
  mutate(Explosives=sum(Weapon=='Explosives'))%>%
  mutate(`Blunt Object`=sum(Weapon=='Blunt object - hammer, club, etc'))%>%
  mutate(`Firearm, type not stated`=sum(Weapon=='Firearm, type not stated'))%>%
  mutate(Rifle=sum(Weapon=='Rifle'))%>%
  mutate(Shotgun=sum(Weapon=='Shotgun'))%>%
  mutate(`Personal Weapons, includes beating`=sum(Weapon=='Personal weapons, includes beating'))%>%
  mutate(`Strangulation - hanging`=sum(Weapon=='Strangulation - hanging'))%>%
  mutate(`Pushed or thrown out window`=sum(Weapon=='Pushed or thrown out window'))%>%
  mutate(Fire=sum(Weapon=='Fire'))%>%
  mutate(`Narcotics or drugs, sleeping pills`=sum(Weapon=='Narcotics or drugs, sleeping pills'))%>%
  mutate(Drowning=sum(Weapon=='Drowning'))%>%
  mutate(`Other gun`=sum(Weapon=='Other gun'))%>%
  mutate(`Asphyxiation - includes death by gas`=sum(Weapon=='Asphyxiation - includes death by gas'))%>%
  mutate(`Poison - does not include gas`= sum(Weapon=='Poison - does not include gas'))

#kable for racial solve rates - uses base table
solve_rate_race <- supp_homi_fips%>%
  mutate(min_year = input$years[1])%>% #Taking max and min year from selected input
  mutate(max_year = input$years[2]) %>%
  #mutate(min_year=2010)%>% #For Testing
  #mutate(max_year=2019)%>% #For Testing
  filter(Year >= min_year & Year <= max_year)%>%
  filter(State==i)%>%
  mutate(count=1)%>%
  group_by(VicRace, Solved)%>% #not grouping by year because it is total solve rate
  mutate(Total=sum(count))%>% #sum of solved/unsolved by race
  select(VicRace, Solved, Total)%>%
  unique()%>%
  ungroup()%>%
  spread(Solved, value=Total) #split into solved and unsolved

#ifelse for when there are no unsolved - creates a no column with 0
ifelse("No" %in% colnames(solve_rate_race),
       
       solve_rate_race <- solve_rate_race %>%
         select(`Victim Race`=VicRace,Unsolved=No,Solved=Yes)%>%           ###PROBLEM WHEN NO UNSOLVED IS HERE
         group_by(`Victim Race`)%>%
         mutate(Unsolved=case_when(is.na(Unsolved)~0, #replacing NAs with 0s
                                   TRUE~Unsolved))%>%
         mutate(Solved=case_when(is.na(Solved)~0,
                                 TRUE~Solved))%>%
         mutate(`Solve Rate`=round((Solved/(sum(Solved, Unsolved)))*100,2)),
       
       solve_rate_race <- solve_rate_race %>%
         mutate(No=0)%>%
         select(`Victim Race`=VicRace,Unsolved=No,Solved=Yes)%>%           ###PROBLEM WHEN NO UNSOLVED IS HERE
         group_by(`Victim Race`)%>%
         mutate(Unsolved=case_when(is.na(Unsolved)~0, #replacing NAs with 0s
                                   TRUE~Unsolved))%>%
         mutate(Solved=case_when(is.na(Solved)~0,
                                 TRUE~Solved))%>%
         mutate(`Solve Rate`=round((Solved/(sum(Solved, Unsolved)))*100,2))
)



#Unsolved by Race and Sex Table
unsolved_race_sex <- select(unsolved_homis, `Female White`,`Male White`, `Unknown White`, `Female A.I./A.N.`,`Male A.I./A.N.`,`Unknown A.I./A.N.`, `Female Black`,`Male Black`,`Unknown Black`,
                            `Female Asian`, `Male Asian`, `Unknown Asian`, `Female Unknown Race`, `Male Unknown Race`, `Unknown Unknown Race`, `Female N.H./P.I.`, `Male N.H./P.I.`, `Unknown N.H./P.I.`) %>%
  gather(`Female White`,`Male White`, `Unknown White`, `Female A.I./A.N.`,`Male A.I./A.N.`,`Unknown A.I./A.N.`, `Female Black`,`Male Black`,`Unknown Black`,
         `Female Asian`, `Male Asian`, `Unknown Asian`, `Female Unknown Race`, `Male Unknown Race`, `Unknown Unknown Race`, `Female N.H./P.I.`, `Male N.H./P.I.`, `Unknown N.H./P.I.`,
         key='Race', value='Count')%>%
  unique()%>%
  mutate(Sex=case_when(grepl('Female',Race)~'Female',      #grepl looks for pattern and then case when assigns it if it finds it
                       grepl('Male',Race)~'Male',          #Assigning sex to split by race and sex
                       grepl('Unknown',Race)~'Unknown'))%>%
  mutate(Race=case_when(grepl('Black',Race)~'Black',
                        grepl('White',Race)~'White',
                        grepl('A.I./A.N.',Race)~'A.I./A.N.',
                        grepl('Asian',Race)~'Asian',
                        grepl('N.H./P.I.',Race)~'N.H./P.I.',
                        grepl('Unknown Race',Race)~'Unknown'))

#creating table for the kable
unsolved_race_sex_kable <- unsolved_race_sex %>%
  mutate(Race=case_when(Race=='A.I./A.N.'~'American Indian or Alaskan Native', #changing the graph abbreviations for the kable
                        Race=='N.H./P.I.'~'Native Hawaiian or Pacific Islander',
                        TRUE~Race))%>%
  select(Race,Sex,Count)%>%
  spread(key=Sex, value=Count)%>% #Split sex into separate columns
  group_by(Race)%>%
  mutate(Total=sum(Female,Male,Unknown))%>%
  ungroup()%>%
  mutate(`% of Unsolved Total`=round(Total/(sum(Total))*100,2))

#breakdown by sex, race, circumstance, weapon
#Table and map?

```

```{r race-sex, warning=FALSE,echo=FALSE, fig.width=6, fig.height=4}

ggplot(data=unsolved_race_sex)+geom_histogram(aes(x=Race, y=Count, fill=Sex), stat='identity', position=position_stack()) +
  #geom_text(aes(x=Race,y=Count, group=Sex, label=Count), position = position_stack(vjust=.5))+   #Removed Numbers due to jumble
  theme_classic() + ggtitle(paste('Figure 2. Unsolved Homicides by Race and Sex',total_homi$min_year[[1]], 'to',total_homi$max_year[[1]])) + ylab('Count') +
  xlab('Reported Victim Race') +
  theme(plot.title = element_text(size=10))

```

```{r text-data-for-fig2, include=FALSE}

#subsets out race and count with highest total
most_race <- unsolved_race_sex_kable%>%
  ungroup()%>%
  top_n(1,Total) #selecting the highest count

most_race[[1]] #subset the Race
most_race[[5]] #subset the Count

most_sex <- unsolved_race_sex%>%
  ungroup()%>%
  group_by(Sex)%>%
  mutate(Sex_Total=sum(Count))%>%
  select(Sex,Sex_Total)%>%
  unique()%>%
  ungroup()%>%
  top_n(1,Sex_Total)

most_sex[[1]] #Subset the Sex
most_sex[[2]] #Subset the Count
```

Figure 2 above shows a breakdown of all unsolved homicides by race and sex. The `r most_race[[1]]` subgroup has the most unsolved homicides among the race subgroups with a total of `r most_race[[5]]`. The `r most_sex[[1]]` subgroup accounts for the most unsolved cases within the sex subgroups with `r most_sex[[2]]`. Table 1 below gives the exact counts by race and sex. These counts are based on the reported victim race for each unsolved homicide case. There may have been more than one victim of a different race, but the race of additional victims is not included in this dataset.


```{r Race-Sex-Table, echo=FALSE,warning=FALSE}

kable(unsolved_race_sex_kable, align = 'c', caption = paste("Unsolved Homicides by Race and Sex from",min_year,"to",max_year))

```

```{r race-solve, echo=FALSE,warning=FALSE}
kable(solve_rate_race, align='c', caption = paste("Solve Rate by Race", min_year, "to",max_year))

```

\newpage

## Murder Weapon - `r total_homi$min_year[[1]]` to `r total_homi$max_year[[1]]`

```{r Murder-Weapon-Tables, include=FALSE}

#taking unsolved homicide table and subsetting murder weapons
murder_weap <- unsolved_homis %>%
  select(Handgun,`Knife or Cutting Instrument`,`Other`,Explosives,`Blunt Object`,`Firearm, type not stated`,Rifle,Shotgun,`Personal Weapons, includes beating`,
         `Strangulation - hanging`,`Pushed or thrown out window`,Fire,`Narcotics or drugs, sleeping pills`,Drowning,`Other gun`,`Asphyxiation - includes death by gas`,
         `Poison - does not include gas`)%>%
  unique()%>%
  gather(Handgun,`Knife or Cutting Instrument`,`Other`,Explosives,`Blunt Object`,`Firearm, type not stated`,Rifle,Shotgun,`Personal Weapons, includes beating`,
         `Strangulation - hanging`,`Pushed or thrown out window`,Fire,`Narcotics or drugs, sleeping pills`,Drowning,`Other gun`,`Asphyxiation - includes death by gas`,
         `Poison - does not include gas`, key='Murder Weapon', value='Count') %>%
  group_by(`Murder Weapon`)%>%
  mutate(`Percent of Unsolved`=round((Count/total_homi$unsolved_homi[[1]])*100,2)) %>% #finding percent of unsolved by weapon
  ungroup()%>%
  arrange(desc(`Percent of Unsolved`))


high_weap <- murder_weap %>%
  filter(Count==max(Count))

high_weap_count <- max(murder_weap$Count)
high_weap_name <- high_weap[[1]]


```

Table 2 below looks at the murder weapons used in unsolved homicides. They are listed in descending order by the highest count. The percent column shows what percentage of unsolved homicides are made up by the murder weapon. Most unsolved homicides in `r i` are committed by `r high_weap_name` with a total of `r high_weap_count`.

```{r Murder-Weapon-Kable}
kable(murder_weap, align="c", caption=paste("Unsolved Homicides by Murder Weapon from",min_year,"to",max_year))
```

\newpage

## Location - `r total_homi$min_year[[1]]` to `r total_homi$max_year[[1]]`

The number of unsolved homicides in each county are totaled and used to create a heat map below. Gray counties represent counties that do not have any unsolved homicides reported. Counties that have higher numbers of unsolved homicides will be bright red and those with less will be lighter shades. Table 4 displays the top 10 counties within `r i` for unsolved homicides.

```{r Map-Tables, include=FALSE}

county_unsolved <- unsolved_homis %>% #using unsolved table - already filtered for unsolved
  mutate(victims = VicCount+1)%>% #0 is used for one victim and anything after counts as additional victims
  mutate(count=1)%>%
  group_by(CNTYFIPS)%>% #grouping by county fips instead of agency - since I will be mapping by county
  mutate(`County Unsolved`=sum(count)) #total of unsolved homicides by county


map_county_allyears <- all_counties %>% #all counties is from tigris is unsolved_run_code script
  left_join(county_unsolved, by=c('GEOID'='county_fips'))%>%
  left_join(state_fips, by=c('STATEFP'='st_fips'))%>% #state_fips is from the census in unsolved_run_code script
  filter(State_Name==i)%>%
  select(State_Name, GEOID, `County Unsolved`, geometry)%>%
  unique()

county_unsolved_kab <- select(county_unsolved, County=CNTYFIPS, `Unsolved Homicide Count`=`County Unsolved`)%>%
  unique()%>%
  arrange(desc(`Unsolved Homicide Count`))

county_unsolved_kab <- county_unsolved_kab[1:10,] %>% #takes the top 10 counties
  filter(!is.na(County)) #removes na counties

```

```{r Unsolved-County-Map}

ggplot(data=map_county_allyears) + geom_sf(aes(fill=`County Unsolved`)) +
  geom_sf_text(aes(label=`County Unsolved`))+
  scale_fill_gradient(low="white",high="red")+
  theme_void() + ggtitle(paste("Map 1. Unsolved Homicides by County -",min_year,"to",max_year)) +
  theme(plot.title = element_text(size=10))

```

```{r Unsolved-County-Kable}
kable(county_unsolved_kab, align="c", caption=paste("Unsolved Homicides by Top 10 Counties from",min_year,"to",max_year))
```

*A full table is available in the appendix

\newpage

## APPENDIX

The table below shows the full unsolved homicide count by counties from `r min_year` to `r max_year`

```{r full_unsolved_county, include=FALSE}
full_county_unsolved_kab <- select(county_unsolved, County=CNTYFIPS, `Unsolved Homicide Count`=`County Unsolved`)%>%
  unique()%>%
  arrange(desc(`Unsolved Homicide Count`))

```

```{r full_kab}
kable(full_county_unsolved_kab)
```

The table below shows the full unsolved homicide count by counties from `r max_year-3` to `r max_year`

```{r recent_unsolved_county, include=FALSE}

unsolved_homis_recent <- supp_homi_fips %>%
  filter(State==i)%>%
  filter(Year >= (max_year-3))%>% #last 3 years
  filter(Solved=='No')%>%
  mutate(Female=sum(VicSex=='Female'))%>%
  mutate(Male=sum(VicSex=='Male'))%>%
  mutate(Unknown=sum(VicRace=='Unknown'))%>%
  mutate(White=sum(VicRace=='White'))%>%
  mutate(`American Indian or Alaskan Native`=sum(VicRace=='American Indian or Alaskan Native'))%>%
  mutate(Black=sum(VicRace=='Black'))%>%
  mutate(Asian=sum(VicRace=='Asian'))%>%
  mutate(`Unknown Race`=sum(VicRace=='Unknown'))%>%
  mutate(`Native Hawaiian or Pacific Islander`=sum(VicRace=='Native Hawaiian or Pacific Islander'))%>%
  #White
  mutate(`Female White`=sum(VicSex=='Female'&VicRace=='White'))%>%
  mutate(`Male White`=sum(VicSex=='Male'&VicRace=='White'))%>%
  mutate(`Unknown White`=sum(VicSex=='Unknown'&VicRace=='White'))%>%
  #AI/NA
  mutate(`Female A.I./N.A.`=sum(VicSex=='Female'&VicRace=='American Indian or Alaskan Native'))%>%
  mutate(`Male A.I./N.A.`=sum(VicSex=='Male' & VicRace=='American Indian or Alaskan Native'))%>%
  mutate(`Unknown A.I./N.A.`=sum(VicSex=='Unknown' & VicRace=='American Indian or Alaskan Native'))%>%
  #Black
  mutate(`Female Black`=sum(VicSex=='Female'&VicRace=='Black'))%>%
  mutate(`Male Black`=sum(VicSex=='Male' & VicRace=='Black'))%>%
  mutate(`Unknown Black`=sum(VicSex=='Unknown'&VicRace=='Black'))%>%
  #Asian
  mutate(`Female Asian`=sum(VicSex=='Female'&VicRace=='Asian'))%>%
  mutate(`Male Asian`=sum(VicSex=='Male' & VicRace=='Asian'))%>%
  mutate(`Unknown Asian`=sum(VicSex=='Unknown' & VicRace=='Asian'))%>%
  #Unknown
  mutate(`Female Unknown Race`=sum(VicSex=='Female'& VicRace=='Unknown'))%>%
  mutate(`Male Unknown Race`=sum(VicSex=='Male'& VicRace=='Unknown'))%>%
  mutate(`Unknown Unknown Race`=sum(VicSex=='Unknown' &VicRace=='Unknown'))%>%
  #NH/PI
  mutate(`Female N.H./P.I.`=sum(VicSex=='Female'&VicRace=='Native Hawaiian or Pacific Islander'))%>%
  mutate(`Male N.H./P.I.`=sum(VicSex=='Male' & VicRace=='Native Hawaiian or Pacific Islander'))%>%
  mutate(`Unknown N.H./P.I.`=sum(VicSex=='Unknown' & VicRace=='Native Hawaiian or Pacific Islander'))%>%
  #Weapons
  mutate(Handgun=sum(Weapon=='Handgun - pistol, revolver, etc'))%>%
  mutate(`Knife or Cutting Instrument`=sum(Weapon=='Knife or cutting instrument'))%>%
  mutate(`Other`=sum(Weapon=='Other or type unknown'))%>%
  mutate(Explosives=sum(Weapon=='Explosives'))%>%
  mutate(`Blunt Object`=sum(Weapon=='Blunt object - hammer, club, etc'))%>%
  mutate(`Firearm, type not stated`=sum(Weapon=='Firearm, type not stated'))%>%
  mutate(Rifle=sum(Weapon=='Rifle'))%>%
  mutate(Shotgun=sum(Weapon=='Shotgun'))%>%
  mutate(`Personal Weapons, includes beating`=sum(Weapon=='Personal weapons, includes beating'))%>%
  mutate(`Strangulation - hanging`=sum(Weapon=='Strangulation - hanging'))%>%
  mutate(`Pushed or thrown out window`=sum(Weapon=='Pushed or thrown out window'))%>%
  mutate(Fire=sum(Weapon=='Fire'))%>%
  mutate(`Narcotics or drugs, sleeping pills`=sum(Weapon=='Narcotics or drugs, sleeping pills'))%>%
  mutate(Drowning=sum(Weapon=='Drowning'))%>%
  mutate(`Other gun`=sum(Weapon=='Other gun'))%>%
  mutate(`Asphyxiation - includes death by gas`=sum(Weapon=='Asphyxiation - includes death by gas'))%>%
  mutate(`Poison - does not include gas`= sum(Weapon=='Poison - does not include gas'))

unsolved_race_sex_recent <- select(unsolved_homis_recent, `Female White`,`Male White`, `Unknown White`, `Female A.I./N.A.`,`Male A.I./N.A.`,`Unknown A.I./N.A.`, `Female Black`,`Male Black`,`Unknown Black`,
                            `Female Asian`, `Male Asian`, `Unknown Asian`, `Female Unknown Race`, `Male Unknown Race`, `Unknown Unknown Race`, `Female N.H./P.I.`, `Male N.H./P.I.`, `Unknown N.H./P.I.`) %>%
  gather(`Female White`,`Male White`, `Unknown White`, `Female A.I./N.A.`,`Male A.I./N.A.`,`Unknown A.I./N.A.`, `Female Black`,`Male Black`,`Unknown Black`,
                            `Female Asian`, `Male Asian`, `Unknown Asian`, `Female Unknown Race`, `Male Unknown Race`, `Unknown Unknown Race`, `Female N.H./P.I.`, `Male N.H./P.I.`, `Unknown N.H./P.I.`,
         key='Race', value='Count')%>%
  unique()%>%
  mutate(Sex=case_when(grepl('Female',Race)~'Female',
                       grepl('Male',Race)~'Male',
                       grepl('Unknown',Race)~'Unknown'))%>%
  mutate(Race=case_when(grepl('Black',Race)~'Black',
                        grepl('White',Race)~'White',
                        grepl('A.I./N.A.',Race)~'A.I./N.A.',
                        grepl('Asian',Race)~'Asian',
                        grepl('N.H./P.I.',Race)~'N.H./P.I.',
                        grepl('Unknown Race',Race)~'Unknown'))

unsolved_race_sex_kable_recent <- unsolved_race_sex_recent %>%
  mutate(Race=case_when(Race=='A.I./N.A.'~'American Indian or Alaskan Native',
                        Race=='N.H./P.I.'~'Native Hawaiian or Pacific Islander',
                        TRUE~Race))%>%
  select(Race,Sex,Count)%>%
  spread(key=Sex, value=Count)%>%
  group_by(Race)%>%
  mutate(Total=sum(Female,Male,Unknown))%>%
  ungroup()%>%
  mutate(`% of Unsolved Total`=round(Total/(sum(Total))*100,2))

full_county_unsolved_yr_disagg <- unsolved_homis_recent %>%
  mutate(count=1)%>%
  group_by(CNTYFIPS, Year)%>%
  mutate(Year_Unsolved=sum(count)) %>%
  ungroup()%>%
  select(County=CNTYFIPS, Year, Year_Unsolved)%>%
  unique()%>%
  spread(`Year_Unsolved`, key="Year")

full_county_unsolved_yr_disagg[is.na(full_county_unsolved_yr_disagg)] <- 0  #Replace NAs with 0

full_county_unsolved_yr_disagg <- full_county_unsolved_yr_disagg%>%
  mutate(`Unsolved Total`=rowSums(full_county_unsolved_yr_disagg[,-1]))%>% #sums all rows except first one - MONEY
  arrange(desc(`Unsolved Total`))
```

```{r full_recent_kab}
kable(full_county_unsolved_yr_disagg)
```
